TrenchR: an R package for transparent environmental and ecological biophysics

### 2022-06-14 ManuscriptTe.Rmd
minor fixes

---
title: "Appendix S1"
author: "Buckley et al."
output:
  html_document: default
  pdf_document: default
  word_document: default
  rmarkdown::html_vignette: default
---

@@

# Biophysical models
```{r, include=FALSE}
#Grasshopper data
setwd("/Volumes/GoogleDrive/Shared drives/TrEnCh/Projects/TrenchR/data/")
spec.dat=read.csv("SpecData.csv")

#read weather data
dat=read.csv("DatAll_Pace2011.csv", sep=",", na.strings = c("-49.99","NA"))
#match site data
sites=read.csv("SiteElevations.csv", sep=",")

@@

```{r, include=FALSE}
setwd("/Volumes/GoogleDrive/Shared drives/TrEnCh/Projects/TrenchR/figures/")

pdf("TeTime2.pdf", height = 10, width = 15)
plot.t
dev.off()

>>>>

---
title: "Appendix S1"
author: "Buckley et al."
output:
  word_document: default
  pdf_document: default
  html_document: default
  rmarkdown::html_vignette: default
---

@@

# Biophysical models
```{r, include=FALSE}
#Grasshopper data
spec.dat=read.csv("./data/SpecData.csv")

#read weather data
dat=read.csv("./data/DatAll_Pace2011.csv", sep=",", na.strings = c("-49.99","NA"))
#match site data
sites=read.csv("./data/SiteElevations.csv", sep=",")

@@

```{r, include=FALSE}
pdf("./figures/TeTime2.pdf", height = 10, width = 15)
plot.t
dev.off()

### 2022-06-14 Manuscript_full.Rmd
minor fixes

The microclimate models indicate that air temperatures at lizard height
are similar to surface temperatures (Figure 2). The biophysical models
indicate that solar radiation will elevate lizard body temperatures far
above air temperatures and that the lizard will face thermal stress if
it is unable to seek shade (Figure 2). The three biophysical models
predict different body temperatures during peak period of solar
radiation because they model interactions with the ground differently
and users are encouraged to review the details of each biophysical model
before selection. Differences in estimated body temperatures are
accentuated by the high level of solar radiation.

@@

**Figure 2**. Body temperatures (Te) are predicted to drastically exceed
air temperature when lizards are exposed to high levels of solar
radiation. Air temperatures (Ta, °C) at lizard height (0.02m) are
predicted to exceed air temperatures at 2m and to be similar to surface
temperatures (Ts). We estimate body temperatures using two general
energy budgets [solid: Tb_Gates(); dotted: Tb_CampbellNorman()] and a
lizard specific biophysical model [dashed: Tb_lizard()] that differ in
how they model heat exchanges.

>>>>

The microclimate models indicate that air temperatures at lizard height
are similar to surface temperatures (Figure 3). The biophysical models
indicate that solar radiation will elevate lizard body temperatures far
above air temperatures and that the lizard will face thermal stress if
it is unable to seek shade (Figure 3). The three biophysical models
predict different body temperatures during peak period of solar
radiation because they model interactions with the ground differently
and users are encouraged to review the details of each biophysical model
before selection. Differences in estimated body temperatures are
accentuated by the high level of solar radiation.

@@

**Figure 3**. Body temperatures (Te) are predicted to drastically exceed
air temperature when lizards are exposed to high levels of solar
radiation. Air temperatures (Ta, °C) at lizard height (0.02m) are
predicted to exceed air temperatures at 2m and to be similar to surface
temperatures (Ts). We estimate body temperatures using two general
energy budgets [solid: Tb_Gates(); dotted: Tb_CampbellNorman()] and a
lizard specific biophysical model [dashed: Tb_lizard()] that differ in
how they model heat exchanges.
